### 2016-11-17 paper/intro.tex
minor changes to intro

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  Dealing with high testing costs is critical at
large IT organizations, with massive code and test bases.  The impact
of the Google TAP system~\cite{google-tap,google-ci} and the Microsoft
CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci} provide
evidence on the criticality of the build and the testing processes at
these organizations.  Note, however, that the regression testing
problem is not specific to giants from the IT sector.  For example, a
recent paper from the automotive industry reported that test suites
can take days to run~\cite{artl-etal-icst2015}.

Several approaches have been proposed in the literature to address the
regression testing problem.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  It is important to note,
however, that balancing the test workload, either within or across
machines, is a popular, sound, and practical approach to address
testing cost and can't be neglected.  Furtheremore, this approach is
complementary to those proposed in the literature. For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.  As additional examples, The Google TAP
system and the Microsoft CloudBuild system distribute the test
workload in the cloud, which is part of their infrastructure.  Note,
that the alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} or even building a
server farm (for increased security) can be a legitimate approach to
mitigate the regression testing problem at large organizations.
However, this solution may not be economically viable for smaller
projects.

>>>>

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  Dealing with high testing costs is critical at
large IT organizations, with massive code and test bases.  The Google
TAP system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci} provide evidence on the
criticality of the build and the testing processes at these
organizations.  Note, however, that the regression testing problem is
not specific to giants from the IT sector.  For example, a recent
paper from the automotive industry reported that test suites can take
days to run~\cite{artl-etal-icst2015}.

Several approaches have been proposed in the literature to address the
regression testing problem.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  It is important to note,
however, that balancing the test workload, either within or across
machines, is a popular, sound, and practical approach to address
testing cost and can't be neglected.  Furtheremore, this approach is
complementary to those proposed in the literature. For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.  As additional examples, Google's TAP
and Microsoft's CloudBuild distribute task workloads in the cloud.
Note, that the alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} or even building a
server farm (for increased security) is a legitimate approach to
mitigate the regression testing problem at large organizations.
However, this solution may not be economically viable for smaller
projects.
